### 2017-12-07 manuscript.rmd
descending/ascending canal simmaps independent in the code

#Mantle canal SIMMAP Setup
#mantle_data = cdata[which(!is.na(cdata$Mantle.Canal)),]
#mantle = mantle_data$Mantle.Canal
#names(mantle)=rownames(mantle_data)
#MantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(mantle))))
#make.simmap(MantleTree, mantle, nsim = 100, message=FALSE) -> mantle_sim
```

@@

```{r mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
#densityMap(mantle_sim)
```

>>>>

#Descending mantle Canal SIMMAP Setup
desc_mantle_data = cdata[which(!is.na(cdata$Desc.Mantle.Canal)),]
desc_mantle = mantle_data$Desc.Mantle.Canal
names(desc_mantle)=rownames(desc_mantle_data)
DescMantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(desc_mantle))))
make.simmap(DescMantleTree, desc_mantle, nsim = 100, message=FALSE) -> desc_mantle_sim

#Ascending Mantle canal SIMMAP Setup
asc_mantle_data = cdata[which(!is.na(cdata$Asc.Mantle.Canal)),]
asc_mantle = mantle_data$Asc.Mantle.Canal
names(asc_mantle)=rownames(asc_mantle_data)
AscMantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(asc_mantle))))
make.simmap(AscMantleTree, asc_mantle, nsim = 100, message=FALSE) -> asc_mantle_sim
```

@@

```{r desc_mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap Descending Mantle Canal
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# desc_mantle_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(desc_mantle_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(desc_mantle_sim)
```

```{r asc_mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap Ascending mantle canal
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# asc_mantle_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(ascribe.simmap(asc_mantle_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(asc_mantle_sim)
```
